---
title: "linear model from Web"
author: "Valerie Rodriguez"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS




### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle ("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size=20))
```

In this scatter plot it's exemplified that the data is showing a simulation of expected arm strength in workers. Disregarding the outliers the majority of the workers had an arm strength level between 50 and 100.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This data explains that relationship between SIMS and ARM is the same. The larger our number is then the larger the correlation between the 2 factors is. 0.686 is a small number showing that there is little correlation.


### Inferential  (Build model.1)




#### Predict at target point





#### scatterplot with model fit
  
  
  
  

## Model 2 SIM~GRIP





### Now add in scatterplot





### Numerical results 





### Inferential  (Build model.2)
  
  
  
  

#### predict model.2 at target point




#### now add the model fit to our plot for model.2
  




## Model 3 SIM~ARM+GRIP






### Numerical results (cor)

`
  
  
  
### Inferential  (Build 2-dimentional model.3)





#### predict model.3 at target point
  





## Comparing nested models ANOVA Test





### Model.1 vs Model.3





### Model.2 vs Model.3






## Informally compare Model.1 with model.2

