---
title: "linear model from Web"
author: "Valerie Rodriguez"
date: "Spring 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS




### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + ggtitle ("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size=20))
```

In this scatter plot it's exemplified that the data is showing a simulation of expected arm strength in workers. Disregarding the outliers the majority of the workers had an arm strength level between 50 and 100.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This data explains that relationship between SIMS and ARM is the same. The larger our number is then the larger the correlation between the 2 factors is. 0.686 is a small number showing that there is little correlation.


### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This is the equation of the line for this data SIMS= 0.054563 x ARM -4.095160. Since we have a positive coefficient the line increases so the plot will move from lower left corner to the up right corner. 

#### Predict at target point

```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)
predict(model.1, tgtpoint, interval= c("prediction"))
```

This data shows that the predicted target plot is 0.7063 but 95% of the time the given value will be in-between -1.7262 and 3.1389.


#### scatterplot with model fit
  
```{r}
basicNN + geom_point() + ggtitle ("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size=20)) + geom_smooth(method=lm)
```

This data plot shows the best fit line from the data collected from SIMS vs. ARM. The line shows which data points are closest to the expected results.  
  

## Model 2 SIM~GRIP


### Now add in scatterplot

```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP)) 
```
```{r}
basicGRIP + geom_point() + ggtitle ("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size=20))
```




### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

In this data with SIMS vs. GRIP the value of 0.6398 is smaller than the value given for SIMS vs. ARM which is 0.6860. This means that the correlation between sims vs grip is less correlated than that of sims vs arms. Sims vs arms is doing a better job at predicting compared to sims vs grip.



### Inferential  (Build model.2)
  
  
  
  

#### predict model.2 at target point




#### now add the model fit to our plot for model.2
  




## Model 3 SIM~ARM+GRIP






### Numerical results (cor)

`
  
  
  
### Inferential  (Build 2-dimentional model.3)





#### predict model.3 at target point
  





## Comparing nested models ANOVA Test





### Model.1 vs Model.3





### Model.2 vs Model.3






## Informally compare Model.1 with model.2

